---
title: "k-means"
author: "restu dn"
date: "4/5/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)

```

```{r}
trainingSet = read.csv('../input/train.csv')

```

```{r}
if(numberOfNA > 0) {
  cat('Number of missing values found: ', numberOfNA)
  cat('\nRemoving missing values...')
  trainingSet = trainingSet[complete.cases(trainingSet), ]
}

```{r}
par(mfrow = c(1, 2))

boxplot(trainingSet$x, main='X', sub=paste('Outliers: ', boxplot.stats(trainingSet$x)$out))

boxplot(trainingSet$y, main='Y', sub=paste('Outliers: ', boxplot.stats(trainingSet$y)$out))

cor(trainingSet$x, trainingSet$y)

regressor = lm(formula = y ~.,
               data = trainingSet)

```

```{r}
ggplot() +
  geom_point(aes(x = trainingSet$x, y = trainingSet$y),
             colour = 'red') +
  geom_line(aes(x = trainingSet$x, y = predict(regressor, newdata = trainingSet)),
            colour = 'blue') +
  ggtitle('X vs Y (Training set)') +
  xlab('X') +
  ylab('Y')
```

```{r}
testSet = read.csv('../input/test.csv')
y_pred = predict(regressor, newdata = testSet)
```

```{r}
ggplot() +
  geom_point(aes(x = testSet$x, y = testSet$y),
             colour = 'red') +
  geom_line(aes(x = trainingSet$x, y = predict(regressor, newdata = trainingSet)),
            colour = 'blue') +
  ggtitle('X vs Y (Test set)') +
  xlab('X') +
  ylab('Y')
```

```{r}
compare <- cbind (actual=testSet$x, y_pred)  # combine actual and predicted
mean (apply(compare, 1, min)/apply(compare, 1, max))
mean(0.9,0.9,0.9,0.9)
```

```{r}
plot(trainingSet$y, resid(regressor), 
     ylab="Residuals", xlab="Price", 
     main="Residual plot") 
mean(regressor$residuals)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)

```

```{r}
trainingSet = read.csv('../input/train.csv')

```

```{r}
if(numberOfNA > 0) {
  cat('Number of missing values found: ', numberOfNA)
  cat('\nRemoving missing values...')
  trainingSet = trainingSet[complete.cases(trainingSet), ]
}

```{r}
par(mfrow = c(1, 2))

boxplot(trainingSet$x, main='X', sub=paste('Outliers: ', boxplot.stats(trainingSet$x)$out))

boxplot(trainingSet$y, main='Y', sub=paste('Outliers: ', boxplot.stats(trainingSet$y)$out))

cor(trainingSet$x, trainingSet$y)

regressor = lm(formula = y ~.,
               data = trainingSet)

```

```{r}
ggplot() +
  geom_point(aes(x = trainingSet$x, y = trainingSet$y),
             colour = 'red') +
  geom_line(aes(x = trainingSet$x, y = predict(regressor, newdata = trainingSet)),
            colour = 'blue') +
  ggtitle('X vs Y (Training set)') +
  xlab('X') +
  ylab('Y')
```

```{r}
testSet = read.csv('../input/test.csv')
y_pred = predict(regressor, newdata = testSet)
```

```{r}
ggplot() +
  geom_point(aes(x = testSet$x, y = testSet$y),
             colour = 'red') +
  geom_line(aes(x = trainingSet$x, y = predict(regressor, newdata = trainingSet)),
            colour = 'blue') +
  ggtitle('X vs Y (Test set)') +
  xlab('X') +
  ylab('Y')
```

```{r}
compare <- cbind (actual=testSet$x, y_pred)  # combine actual and predicted
mean (apply(compare, 1, min)/apply(compare, 1, max))
mean(0.9,0.9,0.9,0.9)
```

```{r}
plot(trainingSet$y, resid(regressor), 
     ylab="Residuals", xlab="Price", 
     main="Residual plot") 
mean(regressor$residuals)
```











